Missing The Point

### 2020-10-16 Manuscript.Rmd
Interpret rhats

@@

@@

@@

These rhat plots all show some initialization before the fifth iteration: is rhat usefull before that??

>>>>

In this plot we observe that $\widehat{R}$ in the chain means generally decreases as a function of the number of iterations---with the exception of an initial increase when $3 < it < 5$. There is no apparent differentiation between the missingness conditions. The mixing between chain means generally improves until $it \geq 30$ to $40$.

@@

The mixing between chain variances mimics the mixing between chain means almost perfectly. Irrespective of the missingness condition, the $\widehat{R}$-values taper off around $it \geq 30$.

@@

With the scientific estimate as parameter we observe very similar $\widehat{R}$-values again. We do, however, see some differentiation between missingness conditions. Conditions with 75% of cases being incomplete show more extreme non-mixing. The overall trend remains the same: about 30 iterations are required before mixing stops improving substantially.

@@

$\widehat{R}$-values in the chains of the novel parameter show a trend similar to the chain means and chain variances. [add something about conditions??]

[These rhat plots all show some initialization before the fifth iteration: is rhat usefull before that??]
